Increasing Productivity in the Domiciliary Care Sector Through Automated Routing and Scheduling of Carers

### 2021-04-20 tex/Pres/main.tex
updated commit.

\title{Increasing Productivity in the Domiciliary Care Sector Through Automated Routing and Scheduling of Carers}
\date{}
\author{A. L. Hawa, C. Lamas-Fernandez, A. Martinez-Sykora, C. Currie, T. Monks, T. Chalklen}
\titlegraphic{\includegraphics[height=1.2cm]{figures/sotonabicare2.png}}
\maketitle

@@

\begin{frame}{Queries}
\scriptsize
%\begin{multicols}{2}
	\begin{itemize}
		\item \note{Desired objective(s)}
		\item Are there skill ``levels'' for carers?
		\item Distinct job types or customised per job
		\item Jobs that \emph{cannot} start late
		\item Lunch breaks
		\item Parking availability at patient's home
		\item PPE/COVID-19 conditions
		\item Frequency of schedule formation
		\item Database/software currently used
		\item Hard and soft constraints
		\item Any additional constraints?
		\item Who will be using the application?
		\item Additional carers available?
	\end{itemize}	
%\end{multicols}
\end{frame}

@@

\begin{frame}{Comparison}
\small
\begin{multicols}{3}	
\begin{block}{Hampshire}
	\begin{itemize}
		\item Carers = 15
		\item Clients = 34
		\item Jobs = 480
	\end{itemize}
\end{block}
\begin{block}{Monmouth}
	\begin{itemize}
		\item Carers = 23
		\item Clients = 47
		\item Jobs = 735
	\end{itemize}
\end{block}
\begin{block}{Aldershot}
	\begin{itemize}
		\item Carers = 9
		\item Clients = 19
		\item Jobs = 184
	\end{itemize}
\end{block}
\end{multicols}	
\end{frame}

@@

\begin{frame}{Comparison: Total Travel Time (minutes)}
\scriptsize
\begin{table}
%\caption{Comparison}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{ccrrcrrcrr}\toprule
	&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
	\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
	\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
	\midrule
	02-Nov && 475.00 & \gre{232.28} && 722.55 & \gre{687.00} && 192.77 & \gre{124.81}\\
	03-Nov && 489.88 & \gre{227.02} && \red{728.62} & 745.88 && 166.05 & \gre{119.21}\\
	04-Nov && 490.77 & \gre{242.58} && \red{769.78} & 895.18 && 178.28 & \gre{119.79}\\
	05-Nov && 490.42 & \gre{271.44} && 798.20 & \gre{687.87} && 211.58 & \gre{122.75}\\
	06-Nov && 479.50 & \gre{243.76} && \red{864.52} & 920.79 && 152.97 & \gre{108.11}\\
	07-Nov && 452.67 & \gre{243.81} && \red{694.07} & 779.27 && 167.70 & \gre{108.08}\\
	08-Nov && 405.41 & \gre{223.68} && \red{666.17} & 802.96 && 176.48 & \gre{119.98}\\
	\bottomrule
\end{tabular}
\end{table}%
\end{frame}

\begin{frame}{Comparison NEW: Total Travel Time (minutes)}
	\scriptsize
	\begin{table}
		%\caption{Comparison}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabular}{ccrrcrrcrr}\toprule
			&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
			\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
			\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
			\midrule
			02-Nov && 372.88 & \gre{232.28} && \red{674.46} & 687.00 && 153.05 & \gre{124.81}\\
			03-Nov && 381.58 & \gre{227.02} && \red{675.89} & 745.88 && 129.47 & \gre{119.21}\\
			04-Nov && 384.52 & \gre{242.58} && \red{722.42} & 895.18 && 141.19 & \gre{119.79}\\
			05-Nov && 389.95 & \gre{271.44} && 745.86 & \gre{687.87} && 168.99 & \gre{122.7}5\\
			06-Nov && 378.22 & \gre{243.76} && \red{824.72} & 920.79 && 123.08 & \gre{108.11}\\
			07-Nov && 356.83 & \gre{243.81} && \red{661.50} & 779.27 && 133.91 & \gre{108.08}\\
			08-Nov && 324.72 & \gre{223.68} && \red{636.07} & 802.96 && 142.60 & \gre{119.98}\\
			\bottomrule
		\end{tabular}
	\end{table}%
\end{frame}

\begin{frame}{Comparison: Total Waiting Time (minutes)}
\scriptsize
\begin{table}
%\caption{Comparison}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{ccrrcrrcrr}\toprule
	&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
	\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
	\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
	\midrule
	02-Nov && \red{1595.00} & 1650.18 && 1407.45 & \gre{1009.16} && \red{222.23} & 260.09\\
	03-Nov && \red{1580.12} & 1665.65 && 1026.38 & \gre{737.81} && 73.95 & \gre{56.53}\\
	04-Nov && \red{1189.23} & 1273.80 && 775.22 & \gre{559.64} && \red{36.72} & 61.53\\
	05-Nov && \red{1159.58} & 1203.28 && 1661.80 & \gre{1527.59} && 338.42 & \gre{332.25}\\
	06-Nov && 1065.50 & \gre{1043.60} && 1505.48 & \gre{1095.16} && 402.03 & \gre{322.17}\\
	07-Nov && \red{957.33} & 1002.54 && 790.93 & \gre{435.51} && \red{212.30} & 212.84\\
	08-Nov && \red{1019.59} & 1089.32 && 548.83 & \gre{322.82} && \red{143.52} & 156.89\\
	\bottomrule
\end{tabular}
\end{table}%
\end{frame}

\begin{frame}{Comparison NEW: Total Waiting Time (minutes)}
	\scriptsize
	\begin{table}
		%\caption{Comparison}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabular}{ccrrcrrcrr}\toprule
			&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
			\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
			\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
			\midrule
			02-Nov && 1697.12 & \gre{1650.18} && 1455.54 & \gre{1009.16} && 261.95 & \gre{260.09}\\
			03-Nov && 1688.42 & \gre{1665.65} && 1079.11 & \gre{737.81} && 110.53 & \gre{56.53}\\
			04-Nov && 1295.48 & \gre{1273.80} && 822.58 & \gre{559.64} && 73.81 & \gre{61.53}\\
			05-Nov && 1260.05 & \gre{1203.28} && 1714.14 & \gre{1527.59} && 381.01 & \gre{332.25}\\
			06-Nov && 1166.78 & \gre{1043.60} && 1545.28 & \gre{1095.16} && 431.92 & \gre{322.17}\\
			07-Nov && 1053.17 & \gre{1002.54} && 823.50 & \gre{435.51} && 246.09 & \gre{212.84}\\
			08-Nov && 1100.28 & \gre{1089.32} && 578.93 & \gre{322.82} && 177.41 & \gre{156.89}\\
			\bottomrule
		\end{tabular}
	\end{table}%
\end{frame}

@@

@@

>>>>

\title{Increasing Productivity in the Domiciliary Care Sector Through Automated Routing and Scheduling of Carers}
\date{}
%\author{A. L. Hawa, C. Lamas-Fernandez, A. Martinez-Sykora, C. Currie, T. Monks, T. Chalklen}
\titlegraphic{\includegraphics[height=1.2cm]{figures/sotonabicare2.png}}
\maketitle

@@

\begin{comment}
\begin{frame}{Queries}
\scriptsize
%\begin{multicols}{2}
	\begin{itemize}
		\item \note{Desired objective(s)}
		\item Are there skill ``levels'' for carers?
		\item Distinct job types or customised per job
		\item Jobs that \emph{cannot} start late
		\item Lunch breaks
		\item Parking availability at patient's home
		\item PPE/COVID-19 conditions
		\item Frequency of schedule formation
		\item Database/software currently used
		\item Hard and soft constraints
		\item Any additional constraints?
		\item Who will be using the application?
		\item Additional carers available?
	\end{itemize}	
%\end{multicols}
\end{frame}

@@

\end{frame}
\end{comment}

\begin{frame}{Comparison: Abicare vs DST}
\small
\begin{multicols}{3}	
\begin{block}{Hampshire}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 15
		\item Clients = 34
		\item Jobs = 480
	\end{itemize}
\end{block}
\begin{block}{Monmouth}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 23
		\item Clients = 47
		\item Jobs = 735
	\end{itemize}
\end{block}
\begin{block}{Aldershot}
	\begin{itemize}
		\setlength{\itemindent}{-.1in}
		\item Carers = 9
		\item Clients = 19
		\item Jobs = 184
	\end{itemize}
\end{block}
\end{multicols}	
\end{frame}

@@

\begin{frame}{Comparison: Total Travel Time (minutes)}
	\scriptsize
	\begin{table}
		%\caption{Comparison}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabular}{ccrrcrrcrr}\toprule
			&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
			\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
			\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
			\midrule
			02-Nov && 372.88 & \gre{232.28} && \red{674.46} & 687.00 && 153.05 & \gre{124.81}\\
			03-Nov && 381.58 & \gre{227.02} && \red{675.89} & 745.88 && 129.47 & \gre{119.21}\\
			04-Nov && 384.52 & \gre{242.58} && \red{722.42} & 895.18 && 141.19 & \gre{119.79}\\
			05-Nov && 389.95 & \gre{271.44} && 745.86 & \gre{687.87} && 168.99 & \gre{122.75}\\
			06-Nov && 378.22 & \gre{243.76} && \red{824.72} & 920.79 && 123.08 & \gre{108.11}\\
			07-Nov && 356.83 & \gre{243.81} && \red{661.50} & 779.27 && 133.91 & \gre{108.08}\\
			08-Nov && 324.72 & \gre{223.68} && \red{636.07} & 802.96 && 142.60 & \gre{119.98}\\
			\bottomrule
		\end{tabular}
	\end{table}%
\end{frame}

\begin{frame}{Comparison: Total Waiting Time (minutes)}
	\scriptsize
	\begin{table}
		%\caption{Comparison}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabular}{ccrrcrrcrr}\toprule
			&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
			\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
			\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
			\midrule
			02-Nov && 1697.12 & \gre{1650.18} && 1455.54 & \gre{1009.16} && 261.95 & \gre{260.09}\\
			03-Nov && 1688.42 & \gre{1665.65} && 1079.11 & \gre{737.81} && 110.53 & \gre{56.53}\\
			04-Nov && 1295.48 & \gre{1273.80} && 822.58 & \gre{559.64} && 73.81 & \gre{61.53}\\
			05-Nov && 1260.05 & \gre{1203.28} && 1714.14 & \gre{1527.59} && 381.01 & \gre{332.25}\\
			06-Nov && 1166.78 & \gre{1043.60} && 1545.28 & \gre{1095.16} && 431.92 & \gre{322.17}\\
			07-Nov && 1053.17 & \gre{1002.54} && 823.50 & \gre{435.51} && 246.09 & \gre{212.84}\\
			08-Nov && 1100.28 & \gre{1089.32} && 578.93 & \gre{322.82} && 177.41 & \gre{156.89}\\
			\bottomrule
		\end{tabular}
	\end{table}%
\end{frame}

@@

%----------------------------------- FIGURES AND PLOTS ------------------------------------%

%=================================== HAMPSHIRE 03 NOV ===================================%

\begin{frame} % HAMPSHIRE 03-NOV nNurses = 11, nJobs = 70, nClients = 28
	\begin{columns}
		\column{0.75\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{35mm}
			\textbf{Hampshire: 03-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{figures/03HampshireAbi}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{figures/03HampshireDST}
		\end{minipage}
		\column{0.25\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			%
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\scriptsize
			\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{-.2in}
				\aitem Total: 91:00:00
				\aitem Travel: 06:21:35
				\aitem Waiting: 28:08:25
				\aitem Distance: 307.63km
			\end{itemize}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\scriptsize
			\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{-.2in}
				\ditem Total: 88:02:41
				\ditem Travel: 03:47:01
				\ditem Waiting: 27:45:39
				\ditem Distance: 153.31km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % PLOTS HAMPSHIRE 03-NOV nNurses = 11, nJobs = 70, nClients = 28
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/3_Nov_20_Hampshire_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/3_Nov_20_Hampshire_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/3_Nov_20_Hampshire_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/3_Nov_20_Hampshire_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%=================================== HAMPSHIRE 06 NOV ===================================%

\begin{frame} % HAMPSHIRE 06-NOV nNurses = 11, nJobs = 71, nClients = 27
	\begin{columns}
		\column{0.75\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{35mm}
			\textbf{Hampshire: 06-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/06HampshireAbi}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/06HampshireDST}
		\end{minipage}
		\column{0.25\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			%
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\scriptsize
			\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{-.2in}
				\aitem Total: 81:15:00
				\aitem Travel: 06:18:13
				\aitem Waiting: 19:26:47
				\aitem Distance: 301.39km
			\end{itemize}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\scriptsize
			\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{-.2in}
				\ditem Total: 76:57:22
				\ditem Travel: 04:03:45
				\ditem Waiting: 17:23:26
				\ditem Distance: 167.34km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % PLOTS HAMPSHIRE 06-NOV nNurses = 11, nJobs = 71, nClients = 27
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Hampshire_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Hampshire_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Hampshire_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Hampshire_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%=================================== MONMOUTH 02 NOV ===================================%

\begin{frame} % MONMOUTH 02-NOV nNurses = 13, nJobs = 102, nClients = 37
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{35mm}
			\textbf{Monmouth:}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/02MonmouthAbi}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\aitem Total: 104:45:00
				\aitem Travel: 11:14:28
				\aitem Waiting: 24:15:32
				\aitem Distance: 497.03km
			\end{itemize}
		\vspace{10mm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{02-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/02MonmouthDST}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\ditem Total: 97:31:10
				\ditem Travel: 11:27:00
				\ditem Waiting: 16:49:10
				\ditem Distance: 569.09km
			\end{itemize}
			\vspace{10mm}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % PLOTS MONMOUTH 02-NOV nNurses = 13, nJobs = 102, nClients = 37
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/2_Nov_20_Monmouth_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/2_Nov_20_Monmouth_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/2_Nov_20_Monmouth_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/2_Nov_20_Monmouth_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%=================================== MONMOUTH 05 NOV ===================================%

\begin{frame} % MONMOUTH 05-NOV nNurses = 16, nJobs = 116, nClients = 40
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{35mm}
			\textbf{Monmouth:}
		\end{minipage}
		\begin{minipage}[c][0.65\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/05MonmouthAbi}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\aitem Total: 120:00:00
				\aitem Travel: 12:25:52
				\aitem Waiting: 28:34:08
				\aitem Distance: 561.90km
			\end{itemize}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{05-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.65\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/05MonmouthDST}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\ditem Total: 115:55:27
				\ditem Travel: 11:27:52
				\ditem Waiting: 25:27:35
				\ditem Distance: 578.20km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % PLOTS MONMOUTH 05-NOV nNurses = 16, nJobs = 116, nClients = 40
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Monmouth_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Monmouth_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Monmouth_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Monmouth_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%=================================== ALDERSHOT 05 NOV ===================================%

\begin{frame} % ALDERSHOT 05-NOV nNurses = 5, nJobs = 30, nClients = 16
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{37mm}
			\textbf{Aldershot:}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.8\linewidth]{figures/05AldershotAbi2}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\aitem Total: 33:20:00
				\aitem Travel: 02:48:59
				\aitem Waiting: 06:21:01
				\aitem Distance: 129.57km
			\end{itemize}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{05-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=0.8\linewidth]{figures/05AldershotDST2}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\ditem Total: 31:45:00
				\ditem Travel: 02:02:25
				\ditem Waiting: 05:32:15
				\ditem Distance: 92.00km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % PLOTS ALDERSHOT 05-NOV nNurses = 5, nJobs = 30, nClients = 16
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Aldershot_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Aldershot_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Aldershot_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/5_Nov_20_Aldershot_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%=================================== ALDERSHOT 06 NOV ===================================%

\begin{frame} % ALDERSHOT 06-NOV nNurses = 5, nJobs = 27, nClients = 15
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\hspace{37mm}
			\textbf{Aldershot:}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/06AldershotAbi}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{Abicare:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\aitem Total: 24:30:00
				\aitem Travel: 02:03:05
				\aitem Waiting: 07:11:55
				\aitem Distance: 98.11km
			\end{itemize}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.05\textheight][c]{\linewidth}
			\textbf{06-Nov-2020}
		\end{minipage}
		\begin{minipage}[c][0.7\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/06AldershotDST}
		\end{minipage}
		\begin{minipage}[c][0.2\textheight][c]{\linewidth}
			\scriptsize
			\hspace{17mm}\textbf{DST:}
			\begin{itemize}
				\setlength{\itemindent}{0.5in}
				\ditem Total: 22:25:16
				\ditem Travel: 01:48:06
				\ditem Waiting: 05:22:10
				\ditem Distance: 83.70km
			\end{itemize}
		\end{minipage}
	\end{columns}
\end{frame}

\begin{frame} % ALDERSHOT 06-NOV nNurses = 5, nJobs = 27, nClients = 15
	\begin{columns}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Aldershot_time_info_abiosrm}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Aldershot_workload_abiosrm}
		\end{minipage}
		\column{0.5\textwidth}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Aldershot_time_info_dst}
		\end{minipage}
		\begin{minipage}[c][0.45\textheight][c]{\linewidth}
			\vspace{5mm}
			\centering
			\includegraphics[width=1\linewidth]{figures/6_Nov_20_Aldershot_workload_dst}
		\end{minipage}
	\end{columns}
\end{frame}

%==========================================================================================

\begin{frame}{Issues}
	\begin{itemize}
		\aitem Missing miles/estimated time for some tasks
		\aitem No travel data (miles/estimated time) between carer's home and first/last tasks
		\aitem Some clients have tasks back-to-back that are given separately - why?
		\aitem All other areas cannot be studied due to missing postcodes
	\end{itemize}
\end{frame}

%==========================================================================================

@@

\begin{comment}
\begin{frame}{Comparison OLD: Total Travel Time (minutes)}
\scriptsize
\begin{table}
%\caption{Comparison}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{ccrrcrrcrr}\toprule
&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
\midrule
02-Nov && 475.00 & \gre{232.28} && 722.55 & \gre{687.00} && 192.77 & \gre{124.81}\\
03-Nov && 489.88 & \gre{227.02} && \red{728.62} & 745.88 && 166.05 & \gre{119.21}\\
04-Nov && 490.77 & \gre{242.58} && \red{769.78} & 895.18 && 178.28 & \gre{119.79}\\
05-Nov && 490.42 & \gre{271.44} && 798.20 & \gre{687.87} && 211.58 & \gre{122.75}\\
06-Nov && 479.50 & \gre{243.76} && \red{864.52} & 920.79 && 152.97 & \gre{108.11}\\
07-Nov && 452.67 & \gre{243.81} && \red{694.07} & 779.27 && 167.70 & \gre{108.08}\\
08-Nov && 405.41 & \gre{223.68} && \red{666.17} & 802.96 && 176.48 & \gre{119.98}\\
\bottomrule
\end{tabular}
\end{table}%
\end{frame}

\begin{frame}{Comparison OLD: Total Waiting Time (minutes)}
\scriptsize
\begin{table}
%\caption{Comparison}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{ccrrcrrcrr}\toprule
&& \multicolumn{2}{c}{Hampshire} && \multicolumn{2}{c}{Monmouth} && \multicolumn{2}{c}{Aldershot} \\
\cmidrule{3-4} \cmidrule{6-7} \cmidrule{9-10}
\multicolumn{1}{c}{Date} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} && \multicolumn{1}{c}{Abicare} & \multicolumn{1}{c}{DST} \\
\midrule
02-Nov && \red{1595.00} & 1650.18 && 1407.45 & \gre{1009.16} && \red{222.23} & 260.09\\
03-Nov && \red{1580.12} & 1665.65 && 1026.38 & \gre{737.81} && 73.95 & \gre{56.53}\\
04-Nov && \red{1189.23} & 1273.80 && 775.22 & \gre{559.64} && \red{36.72} & 61.53\\
05-Nov && \red{1159.58} & 1203.28 && 1661.80 & \gre{1527.59} && 338.42 & \gre{332.25}\\
06-Nov && 1065.50 & \gre{1043.60} && 1505.48 & \gre{1095.16} && 402.03 & \gre{322.17}\\
07-Nov && \red{957.33} & 1002.54 && 790.93 & \gre{435.51} && \red{212.30} & 212.84\\
08-Nov && \red{1019.59} & 1089.32 && 548.83 & \gre{322.82} && \red{143.52} & 156.89\\
\bottomrule
\end{tabular}
\end{table}%
\end{frame}

\begin{figure}
\centering
\begin{subfigure}[h]{0.67\textwidth}
\vspace{3mm}
\includegraphics[width=1\linewidth]{figures/03HampshireAbi}
\caption{Hampshire 03-Nov: Abicare}
\label{fig:03hampabi} 
\end{subfigure}
%\vspace{-10mm}
\begin{subfigure}[h]{0.67\textwidth}
\includegraphics[width=1\linewidth]{figures/03HampshireDST}
\caption{Hampshire 03-Nov: DST}
\label{fig:03hampdst}
\end{subfigure}
\end{figure}
